\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-15 report/paper.tex
boundary condition

\subsection{Boundary conditions}
Dirichlet boundary condition was implemented in order to simulate the fluid inside a bounding box. Dirichlet assumes that the pressure is zero outside the fluid which and therefore the value a quantity has to take along the boundary has to be specified, in this case the velocity was set to zero when a particle reaches the boundary, Bridson~\cite{bridson}.

@@

    % Use ghost-SPH or similar
    To increase the accuracy of the interaction with the boundary and free surfaces a method like ghost-SPH that was presented by Schechter et al.~\cite{ghost} could be implemented.
    A method that Bender et al.~\cite{bender} used was the versatile rigid fluid coupling method for incompressible SPH presented by Akinci et al.~\cite{akinci2012versatile}.
    It is based on static boundary particles which could also be a valid implementation to get better boundary interactions.

    % Parallelize 
    To get the simulation to be able to handle more particles the solution could be parallelized to speed up the calculations.
    This could be done using OpenMP and increasing the threading.

    % Viscosity
    To get the simulation more interesting viscosity can be introduced into the fluid simulation.
    It would make simulations of thicker fluids possible.

>>>>

\subsection{Boundary conditions}
Dirichlet boundary condition was implemented in order to simulate the fluid inside a bounding box. Dirichlet assumes that the pressure is zero outside the fluid and therefore the value a quantity has to take along the boundary has to be specified, in this case the velocity was set to zero when a particle reaches the boundary, Bridson~\cite{bridson}.

An isosurface was also introduced in the middle of the scene in order to simulate collisions with arbitrary objects. This was done in an implicit representation of geometric shapes, as function $f(x,y,z)$. Given an isovalue $C = f(\vect{x})$, point $\vect{x}$ can be classified as follows:

\begin{eqnarray}
\label{eq:classifications}
\begin{array}{ll}
 \mbox{Inside:} & f(\mathbf{x}) < C \\
 \mbox{Outside:} & f(\mathbf{x}) > C \\
 \mbox{On surface:} & f(\mathbf{x}) = C \\  
  \end{array}
\end{eqnarray}

To include all possible implicit geometries can a quadratic function be described as:

\begin{eqnarray}
\label{eqn:quadratic}
f(x,y,z) &=& Ax^2+2Bxy+2Cxz\\
\nonumber &+&2Dx+Ey^2+2Fyz\\
\nonumber &+&2Gy+Hz^2+2Iz\\
\nonumber &+&J
\end{eqnarray}

or on matrix form:

\begin{eqnarray}
\label{eqn:quadricmatrixform}
\mathbf{p}^T\mathbf{Q}\mathbf{p} =  \left[ \begin{array}{cccc} x & y & z & 1 \end{array} \right] \left[ \begin{array}{cccc}
A & B & C &D\\
B & E & F & G\\
C & F & H & I\\
D & G & I & J\\
 \end{array} \right] \left[ \begin{array}{c}x \\
y \\
z \\
1 \end{array} \right]
\end{eqnarray}

Considering that the geometry is placed at the origin, $f(\vect{x}) = 0$ means the particle is on the surface and $\vect{p}^T\vect{Q}\vect{p} \leq 0$ can be used to determine collisions.

Since the quadric surface is known analytically can the differentiation be applied to the quadric directly to get the gradient of the shape in position $\vect{x}$. This gives an efficient and analytical expression with a coefficient matrix $Q$, which is used to determine the new velocity direction of a particle after colliding with the surface.

\begin{eqnarray}
\nabla f(x,y,z)
\label{eqn:quadricnormal}
\nonumber = 2 \left[ \begin{array}{cccc}
A & B & C &D\\
B & E & F & G\\
C & F & H & I\\
 \end{array} \right] \left[ \begin{array}{c}x \\
y \\
z \\
1 \end{array} \right]\\
\nonumber = 2\mathbf{Q}_{sub}\mathbf{p}
\end{eqnarray}

@@

% Use ghost-SPH or similar

% Parallelize
